Gammapy: A Python package for gamma-ray astronomy

### 2023-03-21 src/ms-review.tex
Update IRF figures and text
Signed-off-by: Fabio Pintore <fabio.pintore@inaf.it>
Fix the name of Quentin
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

\author{
	{\it Paper Authors} \and
    Axel Donath \inst{\ref{inst:28}} \and
	Régis Terrier \inst{\ref{inst:20}} \and
	Quentin Rémy \inst{\ref{inst:17}} \and
	Atreyee Sinha \inst{\ref{inst:15}} \and
	Cosimo Nigro \inst{\ref{inst:24}} \and
	Fabio Pintore \inst{\ref{inst:26}} \and
	Bruno Khélifi \inst{\ref{inst:20}} \and
	Laura Olivera-Nieto \inst{\ref{inst:17}}\and
	Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
	\\
	{\it Coordination Committee}\thanks{Corresponding author:
\href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \and
	Fabio Acero \inst{\ref{inst:1}} \and
	David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
	Catherine Boisson \inst{\ref{inst:9}} \and
	Jose Louis {Contreras} \inst{\ref{inst:15}} \and
	Axel Donath \inst{\ref{inst:28}} \and
	Stefan Funk \inst{\ref{inst:19}} \and
	Christopher {van Eldik} \inst{\ref{inst:19}} \and
	Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
	Jim Hinton \inst{\ref{inst:17}} \and
	Bruno Khélifi \inst{\ref{inst:20}} \and
	Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
	Fabio Pintore \inst{\ref{inst:26}} \and
	Régis Terrier \inst{\ref{inst:20}} \and
	Roberta Zanin \inst{\ref{inst:18}} \and
    \\
	{\it Gammapy Project Contributors} \and
	Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
	Pooja Bhattacharjee \inst{\ref{inst:8}} \and
	Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
	Johannes Buchner \inst{\ref{inst:12}} \and
	David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
	Andrew Chen \inst{\ref{inst:14}} \and
	Mathieu {de Bony de Lavergne} \inst{\ref{inst:8}} \and
	José Vinícius {de Miranda Cardoso}\inst{\ref{inst:16}} \and
	Christoph Deil \inst{\ref{inst:17}} \and
	Luca Giunti \inst{\ref{inst:20}} \and
	Léa Jouvin \inst{\ref{inst:32}} \and
	Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
	Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
	Marianne Lemoine-Goumard \inst{\ref{inst:31}} \and
	Jean-Philippe Lenain \inst{\ref{inst:22}} \and
	Maximilian Linhoff \inst{\ref{inst:11}} \and
	Lars Mohrmann \inst{\ref{inst:17}} \and
	Daniel Morcuende \inst{\ref{inst:15}} \and
	Sebastian Panny \inst{\ref{inst:25}} \and
	Maxime Regeard \inst{\ref{inst:20}} \and
	Lab Saha \inst{\ref{inst:15}} \and
	Hubert Siejkowski \inst{\ref{inst:27}} \and
	Aneta Siemiginowska \inst{\ref{inst:28}} \and
	Brigitta M {Sipőcz} \inst{\ref{inst:29}} \and
	Tim Unbehaun \inst{\ref{inst:19}} \and
	Thomas Vuillaume \inst{\ref{inst:8}}
}

>>>>

\author{
	{\it Paper Authors} \and
    Axel Donath \inst{\ref{inst:28}} \and
	Régis Terrier \inst{\ref{inst:20}} \and
	Quentin Remy \inst{\ref{inst:17}} \and
	Atreyee Sinha \inst{\ref{inst:15}} \and
	Cosimo Nigro \inst{\ref{inst:24}} \and
	Fabio Pintore \inst{\ref{inst:26}} \and
	Bruno Khélifi \inst{\ref{inst:20}} \and
	Laura Olivera-Nieto \inst{\ref{inst:17}}\and
	Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
	\\
	{\it Coordination Committee}\thanks{Corresponding author:
\href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \and
	Fabio Acero \inst{\ref{inst:1}} \and
	David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
	Catherine Boisson \inst{\ref{inst:9}} \and
	Jose Louis {Contreras} \inst{\ref{inst:15}} \and
	Axel Donath \inst{\ref{inst:28}} \and
	Stefan Funk \inst{\ref{inst:19}} \and
	Christopher {van Eldik} \inst{\ref{inst:19}} \and
	Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
	Jim Hinton \inst{\ref{inst:17}} \and
	Bruno Khélifi \inst{\ref{inst:20}} \and
	Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
	Fabio Pintore \inst{\ref{inst:26}} \and
	Régis Terrier \inst{\ref{inst:20}} \and
	Roberta Zanin \inst{\ref{inst:18}} \and
    \\
	{\it Gammapy Project Contributors} \and
	Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
	Pooja Bhattacharjee \inst{\ref{inst:8}} \and
	Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
	Johannes Buchner \inst{\ref{inst:12}} \and
	David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
	Andrew Chen \inst{\ref{inst:14}} \and
	Mathieu {de Bony de Lavergne} \inst{\ref{inst:8}} \and
	José Vinícius {de Miranda Cardoso}\inst{\ref{inst:16}} \and
	Christoph Deil \inst{\ref{inst:17}} \and
	Luca Giunti \inst{\ref{inst:20}} \and
	Léa Jouvin \inst{\ref{inst:32}} \and
	Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
	Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
	Marianne Lemoine-Goumard \inst{\ref{inst:31}} \and
	Jean-Philippe Lenain \inst{\ref{inst:22}} \and
	Maximilian Linhoff \inst{\ref{inst:11}} \and
	Lars Mohrmann \inst{\ref{inst:17}} \and
	Daniel Morcuende \inst{\ref{inst:15}} \and
	Sebastian Panny \inst{\ref{inst:25}} \and
	Maxime Regeard \inst{\ref{inst:20}} \and
	Lab Saha \inst{\ref{inst:15}} \and
	Hubert Siejkowski \inst{\ref{inst:27}} \and
	Aneta Siemiginowska \inst{\ref{inst:28}} \and
	Brigitta M {Sipőcz} \inst{\ref{inst:29}} \and
	Tim Unbehaun \inst{\ref{inst:19}} \and
	Thomas Vuillaume \inst{\ref{inst:8}}
}
